### 2020-10-25 Thesis-Chapter3-PolicyMaking.tex
Finish policy lessons section

\subsection{The Classical Analytical Method}

@@

\begin{figure}[h]
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{dfds/build/OODA-classical.png}
  \caption[The Classical Analytical Method]{The Classical Analytical Method}
  \label{fig-classical-method}
\end{figure}

@@

\Ac{incrementalism} is an intuitive and iterative approach posed as an alternative to the \ac{classical-method}.
\Ac{incrementalism} as a policymaking strategy is often referred to as ``\ac{muddling-through}'' after political
scientist Charles Lindblom's classic paper defining and defending the approach \cite{lindblom_muddling_1959}. Written
before Rittel developed the idea of ``\acp{wicked-prob},'' Lindblom nonetheless identified many of the same shortcomings
of the analytical method and sought to formalize the process policymakers were already often using.

@@

There is no \ac{wicked-prob} handbook, but several sources offer advice.

@@

Easy answers, or any solutions that artificially tame the problem, must be rejected.

@@

  \wickedtip{Bring Everyone to the Table}{
}

  \wickedtip{Embrace Flexible, Risk-Based Solutions}{
}

  \wickedtip{Ensure Transparency}{
}

>>>>

\subsection{The Classical Analytic Method}

@@

\begin{figure}[h]
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{dfds/build/OODA-classical.png}
  \caption[The Classical Analytic Method]{The Classical Analytic Method}
  \label{fig-classical-method}
\end{figure}

@@

\Ac{incrementalism} is an intuitive and iterative approach posed as an alternative to the \ac{classical-method}.
\Ac{incrementalism} as a policymaking strategy is often referred to as ``\ac{muddling-through}'' after political
scientist Charles Lindblom's classic paper defining and defending the approach \cite{lindblom_muddling_1959}. Written
before Rittel developed the idea of ``\acp{wicked-prob},'' Lindblom nonetheless identified many of the same shortcomings
of the classical method and sought to formalize the process policymakers were already often using.

@@

Let us define one strategy for handling \ac{wicked-prob} as corralling it back into the classes of problems we are
better at dealing with. That means breaking it into tame sub-problems and developing agreeable strategies for its
irreducibly wicked elements. Once that is done, we can rationally analyze and increment our way to victory. There is no
handbook for how to do this, but several sources offer advice.

@@

Easy answers, or any solutions that artificially tame the problem, will not bring the matter under control. While by
definition there is no step that will truly solve the problem, easy answers deliberately emphasize one value to the
exclusion of others, leaving chaos in those neglected areas. As a result of ignoring root issues feeding the problem,
such solutions are even more likely to produce unintended consequences \cite{commission_tackling_2018}.

@@

  \wickedtip{Bring Everyone to the Table}{

Making sure every relevant group is included is important for two reasons. First, because information is ``uncertain and
diffuse,'' generating an accurate problem statement requires diverse input \cite{rozenshtein_wicked_2018}. Second, for
\ac{incrementalism} to work on the irreducibly wicked roots of the problem, there needs to be some degree of consensus
on overall strategy. Consensus building is not easy among groups with differing values and priorities, but it is
impossible without each group being represented.

  \wickedtip{Unite Problem Definition and Analysis Steps}{

The failures of the \ac{classical-method} and \ac{incrementalism} teach that we must be able to think strategically
while respecting the non-linear nature of \acp{wicked-prob}. One way to use the high level, holistic view of the
classical approach while intertwining the problem definition and analysis steps as in the incrementalist approach. In
practice, this means that the collective understanding of the problem and potential solutions must co-evolve. As Rittel
puts it, ``The systems-approach `of the first generation' [i.e., classical analytics] is inadequate for dealing with
wicked-problems. Approaches of the `second generation' should be based on a model of planning as an argumentative
process in the course of which an image of the problem and of the solution emerges gradually among the participants, as
a product of incessant judgment, subjected to critical argument'' \cite{rittel_dilemmas_1973}.

\wickedtip{Embrace Flexible, Risk-Based Solutions}{

We know that proposals cannot be comprehensively evaluated before or even after implementation, and that each action (or
decision not to act) has irreversible effects. \Ac{incrementalism} is the decision making model to follow here, as it is
inherently responsive to unpredictable changes in the environment. Proposals must therefore be agile. All decisions
involve unknowns, but risk- and uncertainty-management strategies can optimize the expected outcome and maximize the
worst outcome \cite{sunstein_beyond_2015}.

  \wickedtip{Focus Discussion around Concrete Proposals}{

This follows partially from the previous suggestion---problem definition and analysis are combined precisely because the
problem definition depends on the nature of proposed solutions. But this advice deserves emphasis for another reason:
consensus is easier to build around concrete proposals. While debate rages in the abstract, groups are bound to disagree
due to their conflicting values and priorities, but Linblom writes encouragingly about ``the ease with which individuals
of different ideologies often can agree on concrete policy'' in an example about congressional compromise; he goes on to
say, ``Labor mediators report a similar phenomenon: the contestants cannot agree on criteria for settling their disputes
but can agree on specific proposals. Similarly, when one administrator's objective turns out to be another's means, they
often can agree on policy'' \cite{lindblom_muddling_1959}.

% So should I follow my own advice and focus on
%   group_2019 (argues for DAR) and
%   savage_lawful_2018 (a concrete DAR proposal)? -- and related, servan_schreiber_jje_2020

### 2020-10-25 Thesis-Glossary.tex
Finish policy lessons section

\newterm{classical-method}{classical analytical method}{
    A policy making strategy that emphasizes rationalism and functions by setting goals, identifying problems,
    evaluating alternatives, implementing solutions, and analyzing outcomes in order to correct errors
}

>>>>

\newterm{classical-method}{classical analytic method}{
    A policy making strategy that emphasizes rationalism and functions by setting goals, identifying problems,
    evaluating alternatives, implementing solutions, and analyzing outcomes in order to correct errors
}
